How to compute the fusion product of MV cycles in type A

### 2020-12-30 draft.tex
application
Joels changes

The [family of] slices [with $s$-fibre?]
\begin{equation}
    \cW_{\mu_1,\mu_2} = G_1 [t^{-1},(t-s)^{-1}]L_{\mu_1,\mu_2}
\end{equation}
where $L_{\mu_1,\mu_2}\in\Grbd[2]$ is a $\CC[t]$-lattice in $\CC(t)^m$ that specializes to a $\CC\xt$-lattice in $\CC\xT^m$ away from $t = 0$ and away from $t = s$; i.e.\
\begin{equation}
    \label{eq:defWBD}
    \begin{split}
        L_{\mu_1,\mu_2}\otimes \CC[(t-s)^{-1}] = L_{\mu_1,\mu_2}\otimes \CC\xt &= L_{\mu_2} \text{ and } \\
        L_{\mu_1,\mu_2}\otimes\CC[t^{-1}] = L_{\mu_1,\mu_2}\otimes \CC\xt[t-s] &= L_{\mu_1}
    \end{split}
\end{equation}
where $L_{\mu_i}$ denotes the point $t^{\mu_i}G(\cO)\in\Gr$. 
%

The family of semi-infinite orbits \acom{Maybe doesn't make sense before specialization?}
\begin{equation}
    S_{\mu_1,\mu_2} = N_-(\cK) L_{\mu_1,\mu_2}\,. 
\end{equation}

The orbit of $\CC[t]$-lattices in $\CC(t)^m$ whose elements specialize again to $\CC\xt$-lattices in $\CC\xT^m$ away from $t = 0$ and away from $t = s$ as follows
\begin{equation}
    \label{eq:defGrBDlambda}
    \begin{split}
        (\Grbd[2])^{\lambda_1,\lambda_2} = \{L \in\Grbd[2] : L\otimes\CC[t^{-1}] &\in \Gr^{\lambda_2} \text{ and } \\
        L\otimes\CC[(s-t)^{-1}] &\in \Gr^{\lambda_1}\}\,.
    \end{split}
\end{equation}
% 
\acom{These defining conditions are again just telling us that in the fibre over the fixed point $(0,s)\in C^{(2)}$ this set is pairs of lattices; note that we invert the indeterminates $t$ and $(t-s)$ \textit{after} specializing $(0,s)$. Could we give a more explicit characterization like $t^{N_1}(t-s)^{N_2} L_0 \subseteq L\subseteq t^{-N_1}(t-s)^{-N_2}$?}

@@

\begin{proof}
    The proof is fibre by fibre, so fix $s\ne 0$. \acom{Emphasize in the intro later (because this always confuses me) that by the $s$-fibre we really mean the $(0,s)$-fibre; i.e.\ its the BD Grassmannian over the second symmetric power of $C = \AA^1$; better just replace $s$-fibre by $(0,s)$-fibre everywhere it occurs.}
    \begin{enumerate}
        \item The map is well defined. In particular, it defines $\CC[t]$-lattices in $\CC(t)^m$. Moreover, these lattices break down to give pairs of lattices upon inverting $t$ or $t-s$ that have the right properties. [Copy Roger's proof]
        \item The inverse map is got by taking the matrix of multiplication by $t$ on the quotient $\CC[t]^m/L$ just as in the ordinary MVy isomorphism---the only difference being $\CC\xt$ is replaced by $\CC[t]$.
\begin{enumerate}
    \item The matrix of $t$ will have the right block type with respect to the basis 
    \begin{equation}
        \{[e_i],[te_i],\dots,[t^{\mu_{i}-1}e_i] : 1\le i \le m\}
    \end{equation}
    of $\CC[t]^m/t^{\mu_1}(t-s)^{\mu_2}\CC[t]^m$. 
    We can show this if we can show that $\CC[t]$-lattices satisfying Equation~\ref{eq:defWBD} have a basis of the form 
    \begin{equation}
        v_i = t^{\mu_{1,i}}(t-s)^{\mu_{2,i}} + \sum_{j>i} p_{ij}(t) e_j 
    \end{equation}
    with $\deg p_{ij}(t) < \mu_i = \mu_{1,i} + \mu_{2,i}$ ($1\le i\le m$).
    \acom{I don't know why this should be true. We might have to just define fibres of $\cW_{\mu_1,\mu_2}$ in this way?}
    \item $t\big|_{\CC[t]^m/L}$ will have two eigenvalues, 0 and $s$, and its generalized 0-eigenspace will have block type $\le \lambda_1$ while its generalized $s$-eigenspace will have block type $\le \lambda_2$. 
    This should follow from the defining fact that lattices satisfying Equation~\ref{eq:defGrBDlambda} equivalently satisfy 
    \begin{equation}
        \begin{split}
            t\big|_{\CC\xt^m/L_1}\text{ has Jordan type} \le \lambda_1 \\
            t\big|_{\CC\xt^m/L_2}\text{ has Jordan type} \le \lambda_2 
        \end{split}
    \end{equation}
    where recall $L_i = L\otimes \CC[(t-p_i)^{-1}]$ and $p_1 = s$ while $p_2 = 0$. \acom{Somehow, restricting to an eigenspace is like inverting/forgetting the action of $t$ by any other generalized eigenvalue? Basic linear algebra? Joel?}
\end{enumerate}
    \end{enumerate}
\end{proof}

@@

Define $S_{\mu_1,\mu_2}^s = N_-\xT[t^{-1}] t^{\mu_1} (t-s)^{\mu_2}$.

@@

We could also make the following claim. 
\begin{theorem}[Theorem 1 version 2]
    Let $\lambda_1,\lambda_2$ and $\mu$ be dominant, such that $\lambda = \lambda_1 + \lambda_2 \ge \mu$. Then there is an isomorphism 
    \begin{equation}
        \overline{\OO_{\lambda_1,\lambda_2}} \cap \TT_\mu \to \overline{\Grbd[2]^{\lambda_2,\lambda_2}}\cap\cW_\mu 
    \end{equation}
    defined by the same map as in Theorem 1. 
    Note $\cW_\mu = \Gr_\mu$. 
\end{theorem}

@@

\begin{lemma}%[Roger's lemma]
    Let $\mu_1,\mu_2$ be dominant and let $s\in \AA^1 - \{0\}$. Then 
    \begin{equation}
        S_{\mu_1,\mu_2}^s \subset \Gr_\mu 
    \end{equation}
    where $\mu = \mu_1 + \mu_2$.
\end{lemma}

\begin{proof}
    Copy Roger's proof.
\end{proof}

@@

>>>>

%The [family of] slices [with $s$-fibre?]
%\begin{equation}
%    \cW_{\mu_1,\mu_2} = G_1 [t^{-1},(t-s)^{-1}]L_{\mu_1,\mu_2}
%\end{equation}

\begin{equation}
    \cW_\mu = G_1[t^{-1}]L_\mu
\end{equation}

Note that $ L_{\mu_1, \mu_2} = (t-s)^{\mu_2} t^{-\mu_2} L_{\mu} \in \cW_\mu$
and that  $L_{\mu_1,\mu_2}\in\Grbd[2]$ is a $\CC[t]$-lattice in $\CC(t)^m$ that specializes to a $\CC\xt$-lattice in $\CC\xT^m$ away from $t = 0$ and away from $t = s$; i.e.\
\begin{equation}
    \label{eq:defWBD}
    \begin{split}
        %L_{\mu_1,\mu_2}\otimes \CC[(t-s)^{-1}] =
        L_{\mu_1,\mu_2}\otimes \CC\xt &= L_{\mu_2} \otimes \CC\xt \text{ and } \\
        %L_{\mu_1,\mu_2}\otimes\CC[t^{-1}] =
        L_{\mu_1,\mu_2}\otimes \CC\xt[t-s] &= L_{\mu_1} \otimes \CC\xt[t-s]
    \end{split}
\end{equation}
where $L_{\mu_i}$ denotes the point $t^{\mu_i}G(\cO)\in\Gr$. 
%

The family of semi-infinite orbits \acom{Maybe doesn't make sense before specialization?}
\begin{equation}
    S_{\mu_1,\mu_2} = N_-(\CC[t,t^{-1}, (t-s)^{-1}]) L_{\mu_1,\mu_2}\,. 
\end{equation}

The orbit of $\CC[t]$-lattices in $\CC(t)^m$ whose elements specialize again to $\CC\xt$-lattices in $\CC\xT^m$ away from $t = 0$ and away from $t = s$ as follows
\begin{equation}
    \label{eq:defGrBDlambda}
    \begin{split}
        (\Grbd[2])^{\lambda_1,\lambda_2} = \{L \in\Grbd[2] : 
        %L\otimes\CC[t^{-1}] 
        L_{\mu_1,\mu_2}\otimes \CC\xt[t-s] 
        &\in \Gr^{\lambda_2} \text{ and } \\
        % L\otimes\CC[(s-t)^{-1}] 
        L_{\mu_1,\mu_2}\otimes \CC\xt &\in \Gr^{\lambda_1}\}\,.
    \end{split}
\end{equation}
% 
\acom{These defining conditions are again just telling us that in the fibre over the fixed point $(0,s)\in C^{(2)}$ this set is pairs of lattices; note that we invert the indeterminates $t$ and $(t-s)$ \textit{after} specializing $(0,s)$. Could we give a more explicit characterization like $t^{N_1}(t-s)^{N_2} L_0 \subseteq L\subseteq t^{-N_1}(t-s)^{-N_2}$?}

@@

\begin{proof}
    The proof is fibre by fibre, so fix $s\ne 0$. \acom{Emphasize in the intro later (because this always confuses me) that by the $s$-fibre we really mean the $(0,s)$-fibre; i.e.\ its the BD Grassmannian over the second symmetric power of $C = \AA^1$; better just replace $s$-fibre by $(0,s)$-fibre everywhere it occurs.}
    \begin{enumerate}
        \item The map is well defined. In particular, it defines $\CC[t]$-lattices in $\CC(t)^m$. Moreover, these lattices break down to give pairs of lattices upon inverting $t$ or $t-s$ that have the right properties. [Copy Roger's proof]
        \item The inverse map is got by taking the matrix of multiplication by $t$.  More precisely, let $ L \in Gr^{BD} \cap \cW_\mu$.  We work with the quotient $\CC[t]^m/L$ just as in the ordinary MVy isomorphism---the only difference being $\CC\xt$ is replaced by $\CC[t]$.
\begin{enumerate}
    \item 
    We claim that 
    \begin{equation}
        \{[e_i],[te_i],\dots,[t^{\mu_{i}-1}e_i] : 1\le i \le m\}
    \end{equation}
    is a $\CC$-basis of $\CC[t]^m/L$.

    To see this, we use that $ L $ 
 has a $\CC[t]$-basis of the form 
    \begin{equation}
        v_i = t^{\mu_i} + \sum_{j>i} p_{ij}(t) e_j 
    \end{equation}
    with $\deg p_{ij}(t) < \mu_i = \mu_{1,i} + \mu_{2,i}$ ($1\le i\le m$).
    \acom{I don't know why this should be true. We might have to just define fibres of $\cW_{\mu_1,\mu_2}$ in this way?}
    \item $t\big|_{\CC[t]^m/L}$ will have two eigenvalues, 0 and $s$, and its generalized 0-eigenspace will have block type $\le \lambda_1$ while its generalized $s$-eigenspace will have block type $\le \lambda_2$. 
    To see this, note that there is a natural isomorphism
    $$\CC[[t]]^m/(L \otimes_{\CC[t]} \CC[[t]]) = \text{generalized $0$ eigenspace of $t$ on } \CC[t]^m/L$$
    carrying the action of $t $ to the action of $t$.

    The left hand side is the same thing as
    $$ \CC[[t]]^m / (L \otimes_{\CC[t]} \CC[[t]]) = (\CC[t]^m/L) \otimes_{\CC[t]} \CC[[t]] $$

    the defining fact that lattices satisfying Equation~\ref{eq:defGrBDlambda} equivalently satisfy 
    \begin{equation}
        \begin{split}
            t\big|_{\CC\xt^m/L_1}\text{ has Jordan type} \le \lambda_1 \\
            t\big|_{\CC\xt^m/L_2}\text{ has Jordan type} \le \lambda_2 
        \end{split}
    \end{equation}
    where recall 
    $L_i = L\otimes \CC\xt$ ??? 
    % $L_i = L\otimes \CC[(t-p_i)^{-1}]$ 
    and $p_1 = s$ while $p_2 = 0$. \acom{Somehow, restricting to an eigenspace is like inverting/forgetting the action of $t$ by any other generalized eigenvalue? Basic linear algebra? Joel?}
\end{enumerate}
    \end{enumerate}
\end{proof}

Let
$\cW_\mu = G_1[t^{-1}]t^\mu $ and $\hat \cW_\mu = G_1[[t^{-1}]] t^\mu$.

\begin{theorem}[Theorem 1 version 2]
    Let $\lambda_1,\lambda_2$ and $\mu$ 
    %be dominant
    be arbitrary, such that $\lambda = \lambda_1 + \lambda_2 \ge \mu$. Then there is an isomorphism 
    \begin{equation}
        \overline{\OO_{\lambda_1,\lambda_2}} \cap \TT_\mu \to \overline{\Grbd[2]^{\lambda_2,\lambda_2}}\cap\cW_\mu 
    \end{equation}
    defined by the same map as in Theorem 1.
\end{theorem}

@@

\begin{proof}
    Let $ A \in \overline{\OO_{\lambda_1,\lambda_2}}\cap\TT_{\mu_1,\mu_2}^+$ and let $ g $ be the polynomial matrix formed by the Mirkovic-Vybornov isomorphism.  Then the diagonal entries of $ g $ are $ t^{\mu_{1,k}} (t-s)^{\mu_{2,k}}$ and we can factor
    $$ g = (g t^{-\mu_1}(t-s)^{-\mu_2}) t^{\mu_1}(t-s)^{\mu_2} \in N[t, t^{-1}, (t-s)^{-1}] t^{\mu_1} (t-s)^{\mu_2}$$
    So we get containment in one direction.
\end{proof}

% Define $S_{\mu_1,\mu_2}^s = N_-\xT[t^{-1}] t^{\mu_1} (t-s)^{\mu_2}$.

@@

We could also make the following claim.

@@

\begin{lemma}%[Roger's lemma]
    Let $\mu_1,\mu_2$ be dominant and let $s\in \AA^1 - \{0\}$. Then 
    \begin{equation}
        S_{\mu_1,\mu_2}^s \subset \hat \cW_\mu 
    \end{equation}
    where $\mu = \mu_1 + \mu_2$.
\end{lemma}

\begin{proof}
    % Copy Roger's proof.
    We have
\[
\begin{split}
    S_{\mu_1, \mu_2} & = N((t^{-1}))t^{\mu_1}(t-s)^{\mu_2} \\
     & \subset T_1[[t^{-1}]] N((t^{-1})) t^{\mu_1} (t-s)^{\mu_2} \\
     & = T_1[[t^{-1}]] N_1[[t^{-1}]] t^{\mu_1} (t-s)^{\mu_2} \\
     & = B_1[[t^{-1}]] t^{\mu_1} (t-s)^{\mu_2} \\
     & = B_1[[t^{-1}]] t^{\mu_1 + \mu_2} \\
     & \subset G_1[[t^{-1}]] t^{\mu_1 + \mu_2} \\
     & = W_{\mu_1 + \mu_2}
\end{split}
\]
where $B_1[[t^{-1}]] t^{\mu_1} (t-s)^{\mu_2} = B_1[[t^{-1}]] t^{\mu_1 + \mu_2}$ since 
\[
\frac{t}{t-s} = 
1 + \frac{s}{t} + \frac{s^2}{t^2} + \cdots 
\in B_1[[t^{-1}]].
\]
\end{proof}

@@

As an application we can compute fusion of stable MV cycles of type $\alpha_i$ for any $i \in I$. What about more general weights? Having $\kpf > 1$.

\begin{proposition}
    Given two MV cycles $Z_\tau$ and $Z_\sigma$ of type\dots 
    \begin{equation}
        Z_\tau\ast Z_\sigma 
    \end{equation}
    is found by??? 
\end{proposition}
